Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-14 documents/BrazilSlides/slides.tex
Updates from ShareLaTeX
Fixed ShareLatex's overwrite?

\documentclass[
    hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
    xcolor={dvipsnames},
]{beamer}

\usetheme[height=8mm]{Rochester}
\usecolortheme{default}

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\setbeameroption{show notes} % Shows notes on the right of the main slides
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[round]{natbib} % Needed for Author name citations
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots

@@

\begin{frame}[allowframebreaks]
    \frametitle{References}
    \todo[TC]{Figure out how to get references at the end}
    \setbeamertemplate{bibliography item}{\insertbiblabel}
    \bibliographystyle{plainnat}
    \bibliography{../references}{}
\end{frame}

@@

\begin{frame}
    \frametitle{Objective Cont'd}
    \begin{itemize}
        \item In~\citet{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
        \item In~\citet{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
        \item In~\citet{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
    \end{itemize}
    \note[item]{At the time of publishing~\citet{Branciard_2012}, problem seems hard.}
    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
\end{frame}

@@

>>>>

\documentclass[
    hyperref={bookmarks=false},% ,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue
    xcolor={dvipsnames},
]{beamer}

\usetheme[height=8mm]{Rochester} % Main Theme
\usecolortheme{default} % Color Theme

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\setbeameroption{show notes} % Shows notes on the right of the main slides
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
% \usepackage[round]{natbib} % Needed for Author name citations
\usepackage[backend=biber]{biblatex} %
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
\setbeamertemplate{bibliography item}{\insertbiblabel}
\addbibresource{../references.bib}

@@

@@

\begin{frame}
    \frametitle{Objective Cont'd}
    \begin{itemize}
        \item In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
        \item In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
        \item In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
    \end{itemize}
    \note[item]{At the time of publishing~\cite{Branciard_2012}, problem seems hard.}
    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
\end{frame}

@@

\begin{frame}[allowframebreaks]
    \frametitle{References}
    \todo[TC]{Figure out how to get references at the end}
    \printbibliography
\end{frame}
